---
title: "Index.Rmd"
author: "Yuki"
date: "2019/2/18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("civic-info.R")
source("propublica.R")
library("knitr")
```

## api-report
## Your Representatives
This is a report about the political representatives based on the address entered (`r address`). This report draws upon data from the ProPublica API and the Google Civic Data API.
As an overview, here is a summary of who represents the address given (from the local to the
national level).

```{r results='asis', echo = FALSE}
kable(summary)
```

## House of Representatives
Now let’s take a look at all of the congressional representatives (in the House of Representatives,
not the Senate) for the state in which the address was given. We see this breakdown by gender
and political party for those members of the House:

```{r echo = FALSE}
plot(plot_gen)
```

```{r echo = FALSE}
plot(plot_par)
```

## `r name`
Let’s learn a bit more about one representative, `r name`. The representative is `r age` years
old, and you can find them on twitter at [`r name`](`r twitter_link`). Interestingly, of the last 20
congressional votes, the representative was in accordance with the majority `r accordance_rate`% of the time.

